INTELLIGENT SYSTEMS

### 2021-03-15 slides.tex
finish slides paper1

\begin{frame}{EXPERIMENTS}

\end{frame}

>>>>

\begin{frame}[t]{EXPERIMENTS}
    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
    btained by the systems already existing at the state of the art.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
        \centering
        \caption{Metrics comparison.}
        \label{fig: metrics}
    \end{figure}
\end{frame}

\begin{frame}{DISCUSSION}
    It is necessary to say that the results obtained by the proposed method 
    are obtained using the center bias, which if removed places the system 
    performance under those of systems such as \emph{RF} \footfullcite{0747815518} and \emph{HS}\footfullcite{0747815508} (which do not 
    use the central bias). This method offers a dual use. In 
    a cluttered scene with no dominant objects, the system will function as a 
    fixation prediction model. Finally, on the other hand, with simple scenes, 
    the system detects existing relevant objects.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.7 \linewidth]{paper1/SystemsComp.png}
        \centering
        \label{fig: metrics}
    \end{figure}
\end{frame}
